PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-06-08 manuscript_00.Rmd
more diff tweaking

```{r}
spec_diff <- diff_tab_big %>% 
  filter(Symbol %in% diff_tab$Symbol) %>% # only retain diff genes across "All"
  group_by(Symbol, Organism, Base) %>% 
  summarise(Count = n()) %>% 
  filter(Count > 1) %>% summarise(Count = n()) %>% filter(Count < 3) %>% mutate(go = paste(Symbol, '___', Organism, sep = '')) %>% pull(go)

diff_tab_big %>% 
  filter(Symbol %in% diff_tab$Symbol) %>% # only retain diff genes across "All"
  group_by(Symbol, Organism, Base) %>% 
  summarise(Count = n()) %>% 
  filter(Count > 1) %>% mutate(go = paste(Symbol, '___', Organism, sep = '')) %>% 
  filter(go %in% (spec_diff))  %>% 
  select(-go) %>% 
  ungroup() %>% 
  group_by(Organism, Base) %>% 
  slice_max(n = 10, order_by = Count) %>% 
  filter(Base == 'Rod')
```

>>>>

```{r}
spec_diff <- diff_tab_big %>% 
  filter(Symbol %in% diff_tab$Symbol) %>% # only retain diff genes across "All"
  group_by(Symbol, Organism, Base) %>% 
  summarise(Count = n()) %>% 
  summarise(Count = n())

spec_diff_go <- spec_diff %>% 
  filter(Count <= 3) %>% 
  mutate(go = paste(Symbol, '___', Organism, sep = '')) %>% 
  pull(go)

diff_tab_big %>% 
  filter(Symbol %in% diff_tab$Symbol) %>% # only retain diff genes across "All"
  group_by(Symbol, Organism, Base) %>% 
  summarise(Count = n(),
            baseMean = mean(baseMean),
            log2FoldChange = mean(log2FoldChange),
            padj = mean(padj)) %>% 
  filter(Count > 1) %>% 
  left_join(spec_diff, by = c("Symbol", "Organism")) %>% 
  mutate(Ratio = `Count.x` / `Count.y`) %>% 
  select(-`Count.x`,-`Count.y`) %>% 
  #mutate(go = paste(Symbol, '___', Organism, sep = '')) %>% 
  #filter(go %in% (spec_diff_go))  %>% 
  #select(-go) %>% 
  ungroup() %>% 
  group_by(Organism, Base) %>% 
  slice_max(n = 10, order_by = log2FoldChange)

### heatmap
```{r, fig.width=5, fig.height=20}
diff_ratios <- diff_tab_big %>% 
    filter(Against != 'All') %>% 
    group_by(Symbol, ID, Organism, Base) %>% 
    summarise(Count = n()) %>% 
    filter(Count > 1) %>% 
    left_join(spec_diff, by = c("Symbol", "Organism")) %>% 
    mutate(Ratio = `Count.x` / `Count.y`) %>% 
    select(Symbol:Base, Ratio)

gene_sets <- diff_tab %>% 
  left_join(diff_ratios, by = c('Symbol', 'ID','Base','Organism')) %>% 
  filter(Ratio > 0.2) %>% group_by(Base, Organism) %>% 
  slice_max(n=20, order_by = log2FoldChange)

g <- gene_sets %>% filter(Organism == 'Homo sapiens') %>%  mutate(gk = paste0(Symbol, ' (', ID, ')')) %>% pull(gk) %>% unique()

x <- scEiaD_2020_v01 %>% tbl("diff_testing") %>% filter(Gene %in% g) %>% collect() %>% filter(Group == 'CellType (Predict)', Organism == 'Homo sapiens', Against == 'All') %>% select(Gene, log2FoldChange, Base) %>% pivot_wider(values_from=log2FoldChange, names_from = Base) 
celltype <- colnames(x[,-1])
x <- x %>% data.frame()
row.names(x) <- x$Gene
x <- x[,-1]
Heatmap(x, column_labels = celltype)
```
